CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability and GPUs

### 2019-03-22 gpus/paper.tex
update bib style
updates

%\documentclass[12pt, preprint]{aastex}
\documentclass[twocolumn,times]{aastex62}
%\documentclass[preprint,times]{aastex6}

@@

\usepackage{epsf,color,amsmath}

@@

\castro\ development began with \cite{castro}, with the goal of
creating an astrophysical hydrodynamics code using a modern adaptive
mesh refinement library with space- and time-refinement (BoxLib at the
time) and unsplit hydrodynamics techniques.  \castro\ now uses the
AMReX adaptive mesh refinement library to handle the computational
grid, memory management, and parallelism, and the \castro\ and AMReX
developers work closely together to The initial application area was
nuclear astrophysics, including core-collapse supernovae, so it was
designed to work with a general equation of state~\cite{zingalekatz}
and arbitrary nuclear reaction networks, and with radiation transport
(through flux limited diffusion, \citealt{castro2,castro3}).  It
includes full self-gravity using multigrid methods with isolated
boundaries \citep{katz:2016}.  Finally, \castro\ also acted as the
compressible counterpart to our low Mach number hydrodynamics code
\maestro, sharing much of the same infrastructure, and allowing for
simulations to be restarted from the low Mach regime into the
compressible regime~\cite{malone:2014}.

@@

The {\tt flame\_wave} problem in \castro\ was described in
\cite{astronum:2018}.  This problem explores the lateral propagation
of a helium deflagration across a neutron star in a plane-parallel
atmosphere.  The Castro PPM CTU hydrodynamics solver is used, with a
constant gravitational acceleration, and the problem is solved in the
corotating frame, where the Coriolis forces acts to balance the
lateral spreading in the atmosphere via geostrophic balance.  For the
microphysics, we use the general stellar equation of state of
\cite{timmes_swesty:2000} and the stellar conductivity described in
\cite{Timmes00}.  The science goal of the problem is to understand the
dynamics of a resolved burning front in X-ray bursts.  For this work,
this problem serves as an ideal reacting flow problem to benchmark
GPUs with.  All of the necessary physics: hydrodynamics, equation of
state, thermal conductivities, reactions, hydrodynamic source terms,
and thermal diffusion are run on the GPU.  We look at two different
reaction networks, a 7-isotope alpha network and a 13-isotope alpha
network~\cite{iso7}.

@@

\bibliographystyle{apj}
\bibliography{ws}

>>>>

\documentclass[twocolumn,times]{aastex62}

@@

\usepackage[T1]{fontenc}
\usepackage{epsf,color,amsmath}

@@

\castro\ development began with \cite{castro}, with the goal of
creating an astrophysical hydrodynamics code using a modern adaptive
mesh refinement library with space- and time-refinement (BoxLib at the
time) and unsplit hydrodynamics techniques.  \castro\ now uses the
AMReX adaptive mesh refinement library to handle the computational
grid, memory management, and parallelism, and the \castro\ and AMReX
developers work closely together to The initial application area was
nuclear astrophysics, including core-collapse supernovae, so it was
designed to work with a general equation of state~\citep{zingalekatz}
and arbitrary nuclear reaction networks, and with radiation transport
(through flux limited diffusion, \citealt{castro2,castro3}).  It
includes full self-gravity using multigrid methods with isolated
boundaries \citep{katz:2016}.  Finally, \castro\ also acted as the
compressible counterpart to our low Mach number hydrodynamics code
\maestro, sharing much of the same infrastructure, and allowing for
simulations to be restarted from the low Mach regime into the
compressible regime~\citep{malone:2014}.

@@

The {\tt flame\_wave} problem in \castro\ was described in
\cite{astronum:2018}.  This problem explores the lateral propagation
of a helium deflagration across a neutron star in a plane-parallel
atmosphere.  The Castro PPM CTU hydrodynamics solver is used, with a
constant gravitational acceleration, and the problem is solved in the
corotating frame, where the Coriolis forces acts to balance the
lateral spreading in the atmosphere via geostrophic balance.  For the
microphysics, we use the general stellar equation of state of
\citep{timmes_swesty:2000} and the stellar conductivity described in
\citep{Timmes00}.  The science goal of the problem is to understand the
dynamics of a resolved burning front in X-ray bursts.  For this work,
this problem serves as an ideal reacting flow problem to benchmark
GPUs with.  All of the necessary physics: hydrodynamics, equation of
state, thermal conductivities, reactions, hydrodynamic source terms,
and thermal diffusion are run on the GPU.  We look at two different
reaction networks, a 7-isotope alpha network and a 13-isotope alpha
network~\cite{iso7}.

@@

\bibliographystyle{aasjournal}
\bibliography{ws}
